Manuscript

### 2015-05-29 inst/simulation/manuscript.Rmd
...

```{r figure-5}
getCIProportions <- function(scenarios, modelNames, panel, scenarioNames, cutoff=Inf) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeCutoff=cutoff)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  credibilityIntervals$panel <- panel
  credibilityIntervals$scenario <- rep(scenarioNames, times=2, each=length(modelNames))
  return(credibilityIntervals)  
}

>>>>

```{r figure-5}
getCIProportions <- function(scenarios, modelNames, panel, scenarioNames, cutoff=Inf) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeCutoff=cutoff)
  credibilityIntervals <- list()

  if ("FMPModel" %in% modelNames) {
    modelNames <- modelNames[!modelNames %in% "FMPModel"]

    for (scenario in scenarios) {
      study <- getStudy(scenario=scenario)
      validation <- Validation(study=study, populationSizeCutoff=cutoff)
      iterations <- validation$getCredibilityIntervalsValidationIterations("FMPModel")
      p95 <- c()
      p50 <- c()
      for (i in iterations) {
        load(file=validation$getCredibilityIntervalsValidationFileName(modelName=modelName, iteration=i))
        p95 <- c(p95, bootCI$p95)
        p50 <- c(p50, bootCI$p50)
      }
      a <- data.frame(scenario=scenario, Proportion=mean(p95, na.rm=T), n=NA, True=NA, Estimated=NA, Estimated.q1=NA, Estimated.q2=NA, modelName="FMPModel", Interval="95%")
      b <- data.frame(scenario=scenario, Proportion=mean(p50, na.rm=T), n=NA, True=NA, Estimated=NA, Estimated.q1=NA, Estimated.q2=NA, modelName="FMPModel", Interval="50%")
      credibilityIntervals <- rbind(credibilityIntervals, rbind(a, b))
    }
  }

  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  #credibilityIntervals <- rbind(a, b)
  credibilityIntervals <- rbind(credibilityIntervals, rbind(a, b))
  credibilityIntervals$panel <- panel
  credibilityIntervals$scenario <- rep(scenarioNames, times=2, each=length(modelNames))
  return(credibilityIntervals)  
}
